\section{Discussions}\label{sec:discuss}

This section discusses \xxx's limitations (\S\ref{sec:limits}) and its broad 
applications (\S\ref{sec:apps}).

\subsection{Limitations}\label{sec:limits}

% P1: Soundness and completeness
% State the main goal of our tool: scalable to large code and accurate. Neither
% sound or complete.
\xxx's main design goal is to achieve reasonable accuracy and scalability, 
and it trades off soundness (\ie, do not miss any bugs), although \xxx did not 
missed the evaluated attacks (\S\ref{sec:known-attacks}). A typical way to 
ensure soundness is to plug in a sound alias analysis tool (\eg,~\cite{bddbddb, 
dsa:pldi07}) to identify all LLVM \v{load} and \v{store} instructions that may 
access the same memory. However, typical alias analyses are known to be 
inaccurate (\eg, too many false positives).
% \xxx can leverage advanced precise 
% alias analysis techniques~\cite{peregrine:sosp11, wu:pldi12, chimera:pldi12} to 
% improve soundness, and we leave it for future work.

% P2: Vulnerability site; limited, external functions.
\xxx currently handles five types of regular vulnerability operations 
(\S\ref{sec:patterns}), and it requires these operations to exist in the LLVM 
bitcode. These five types of operations are sufficient to cover all 
\nreproduced concurrency attacks we have reproduced, and more types can be 
added. If developers are concerned about some library code that may contain 
vulnerabilities, they should compile this code into the bitcode for \xxx.

% P3: Static, can not figure out the exact value without actual executions. For 
% example, branches taken to avoid vulnerabilities, pointer dereference values 
% depending on inputs.
\xxx's consequence analysis tool integrates the call stack of a concurrency bug to 
direct static analysis toward vulnerable program paths, but \xxx's vulnerable 
input hints (\S\ref{sec:algo}) may contain false reports (\eg, the outcomes 
in \xxx's collected bug-to-attack propagation branches may have conflicts). 
Developers can inspect the propagation chains and refine their program inputs to 
validate the outcomes. In our evaluation, we found these input hints expressive 
as they helped us identify subtle inputs for real 
attacks (\S\ref{sec:known-attacks}).




% False negative:
% 1. No alias analysis. Focus on describing the limitations of alias: too many 
% false positives, false negatives, and buggy.


% False positive:
% 1. library functions that couldn't obtain source code.
% 2. data flow analysis is path insensitive
% 3. data flow analysis is flow insensitive
% 4. Static, can not figure out the exact value without actual executions. For 
% example, branches taken to avoid vulnerabilities, pointer dereference values 
% depending on inputs.

\subsection{\xxx has Broad Applications}\label{sec:apps}

% Spur new tools for concurrency attacks. Work with anormaly detections. Work 
% with process race detections.
We envision two immediate applications for \xxx's techniques. First, \xxx can 
augment existing defense tools on concurrency attacks. For instance, we can 
leverage anomaly detection~\cite{schonberg:pldi89, 
taskrecycling:ppopp90,diduce:icse02} and intrusion 
detection~\cite{hofmeyr:syscall:ids, wagner:syscall:ids, wagner:intrusion} tools 
to audit only the vulnerable program paths identified by \xxx, then these 
runtime detection tools can greatly reduce the amount of program paths that need 
to be audited and improve performance. \xxx can also integrate with other bug 
detection tools (\eg, process races~\cite{racepro:sosp11} and atomicity 
bugs~\cite{ctrigger:asplos09}) to detect concurrency attacks caused by such 
bugs.

Second, \xxx's consequence analysis tool has the potential to detect various 
consequences of software bugs. Software bugs have 
caused many extreme disasters~\cite{10-historical-bug-consequences, 
10-epic-software-bugs} in the last few decades, including losing big money and 
taking lives. By adding new vulnerability and failure sites of such 
consequences, \xxx can be applied to flagging bugs that can cause severe 
consequences among enormous bug reports.

% Third, \xxx's techniques can be applied to detect general concurrency bugs. 
% Both static and dynamic concurrency bug detectors are prone to false positives, 
% and inspecting these reports have caused too much manpower and money. 
% \xxx's false positive filters and analysis tool may mitigate these issues.
