\section{Related Work} \label{sec:related}


\para{TOCTOU attacks.} 
Time-Of-Check-to-Time-Of-Use attacks~\cite{bishop:tocttou,toctou:fast08, 
toctou:fast05,toctou:usec03} target 
mainly the file interface, and leverage atomicity violation on 
time-of-check (\texttt{access()}) and time-of-use (\texttt{open()}) of
a file to gain illegal file access.

A prior concurrency attack study~\cite{con:hotpar12} elaborates that 
concurrency attacks are much broader and more difficult to track than TOCTOU 
attacks for two main reasons. First, TOCTOU mainly causes illegal file access, 
while concurrency attacks can cause a much broader range of security 
vulnerabilities, ranging from gaining root privileges~\cite{uselib-bug-12791}, 
injecting malicious code~\cite{freebsd-exploit-2009-3527}, to corrupting 
critical memory~\cite{apache-bug-25520}. Second, concurrency attacks stem from 
miscellaneous memory accesses, and TOCTOU stem from file accesses, 
thus handling concurrency attacks is much more difficult than TOCTOU.

% Our study in this paper differs from prior study~\cite{con:hotpar12} via 
% constructing actual inputs and scripts to trigger \nreproduced concurrency 
% attacks, and via deeply looking into their input patterns, source-level bug 
% patterns, and efficacy of existing race detection tools. This paper 
% also presents \xxx, the first analysis framework to detect concurrency attacks.

\para{Sequential security techniques.} Defense techniques for sequential
programs are well studied, including
taint tracking~\cite{taintdroid:osdi10,
lift:micro06,myers:information,valgrind:pldi}, anomaly
detection~\cite{taskrecycling:ppopp90,schonberg:pldi89}, address space
randomization~\cite{ aslr-fail:ccs04}, and static
analysis~\cite{seth:pldi,engler:vmcai,wagner:syscall:ids,coverity:cacm,
klee:osdi08}.

However, with the presence of multithreading, most existing sequential defense 
tools can be largely weakened or even completely bypassed~\cite{con:hotpar12}. For 
instance, concurrency bugs in global memory may corrupt metadata tags in 
metadata tracking techniques. Anomaly detection lacks a concurrency model to 
reason about concurrency bugs and attacks.
% Static analysis has shown to find 
% numerous bugs in real-world programs, however, when facing a program's huge 
% amount of functions, program paths, and possible thread interleavings, static 
% analysis usually reports too many false positives and bury the real ones 
% (\S\ref{sec:study}).

% \para{Program slicing.}  Program slicing~\cite{Tip:slicing} is a
% general technique to prune irrelevant statements from a program or trace.
% Recently, systems researchers have leveraged or invented slicing
% techniques to block malicious input~\cite{castro:bouncer}, synthesize
% executions for better error diagnosis~\cite{esd:eurosys10}, infer source
% code paths from log messages for postmortem analysis~\cite{sherlog:asplos10}, 
% and identify critical inter-thread reads that may lead to concurrency 
% errors~\cite{conseq:asplos11}.

\para{Concurrency reliability tools.} Various prior systems work on 
concurrency bug 
detection~\cite{yu:racetrack:sosp,savage:eraser,racerx:sosp03,lu:muvi:sosp,
avio:asplos06,conmem:asplos10,conseq:asplos11,racemob:sosp13,
wester:parallelizing:asplos13},
diagnosis~\cite{racefuzzer:pldi08,
ctrigger:asplos09,atomfuzzer:fse08,xray:osdi12,gist:sosp15}, and
correction~\cite{dimmunix:osdi08,gadara:osdi08,wu:loom:osdi10,cfix:osdi12}.
They focused on concurrency bugs themselves, while \xxx focuses on the security 
consequences of concurrency bugs. Therefore, these systems are complementary to 
\xxx.

% Benjamin el~\cite{wester:parallelizing:asplos13} presents a parallel data race 
% detection system by replaying program executions with race detections on 
% multi-core. This approach has shown to speed up race detections by about 4X 
% on multi-core hardware. This approach is complementary to \xxx because \xxx 
% focuses on reducing the excessive amounts of race reports to identify the 
% vulnerable ones. \xxx can leverage this parallel detection approach to further 
% speed up its concurrency attack detection in the reduced reports.

Conseq~\cite{conseq:asplos11} detects harmful concurrency bugs by analyzing its 
failure consequence. Its key observation is that concurrency bugs and the bugs' 
failure sites are usually within a short control and data flow propagation 
distance (\eg, within the same function). Concurrency attacks targeted in \xxx 
usually exploit corrupted memory that resides in different functions, thus 
Conseq is inadequate for concurrency attacks. Conseq's proactive harmful 
schedule exploration technique will be useful for \xxx to trigger more 
vulnerable schedules.

% Unlike \xxx's forward propagation analysis, Conseq starts form a 
% failure site and goes backward to detect concurrency bugs. The reason is 
% because Conseq observes that concurrency bugs often have short propagation 
% distances to their failure sites. Conseq's analysis works well because: (1) 
% this distance is short, and (2) Conseq aims to detect concurrency bugs. 
% If the distance is long, backward analysis may have low scalability or 
% accuracy. \xxx does forward analysis because we aim to detect 
% concurrency attacks from the excessive bug reports and we observed that 
% concurrency bugs and their attacks often have long propagations (\eg, 
% across different functions).

\para{Static vulnerability detection tools.} There are already a 
variety of static vulnerability detection 
approaches~\cite{livshits05finding,yamaguchi:sp14,felmetsger:usec10,
flowdroid:pldi14,srivastava:pldi11,zhang:usenix:sec02}. 
These approaches fall into two categories based on whether they 
target general or specific programs.

The first category~\cite{livshits05finding,yamaguchi:sp14} targets general 
programs and their approaches have been shown to find severe vulnerabilities in large 
code. However, these pure static analyses may not be adequate to cope with 
concurrency attacks. Benjamin et al.~\cite{livshits05finding} leverages pointer 
analysis to detect data flows from unchecked inputs to sensitive sites. 
This approach ignores control flow and thus it is not suitable to track 
concurrency attacks like the \libsafe one in \S\ref{sec:example}. Yamaguchi 
et al.~\cite{yamaguchi:sp14} did not incorporate inter-procedural analysis and thus 
is not suitable to track concurrency attacks either. Moreover, these general 
approaches are not designed to reason about concurrent behaviors 
(\eg,~\cite{yamaguchi:sp14} can not detect data races).

\xxx belongs to the first category because it targets general 
programs. Unlike the prior approaches in this category, \xxx incorporates 
concurrency bug detectors to reason about concurrent behaviors, and \xxx's 
consequence analyzer integrates critical dynamic information (\ie, call stacks) 
into static analysis to enable comprehensive data-flow, control-flow, 
and inter-procedural analysis features.

The second category~\cite{felmetsger:usec10,
flowdroid:pldi14,srivastava:pldi11,zhang:usenix:sec02} lets static analysis 
focus on specific behaviors (\eg, APIs) in specific programs to achieve 
scalability and accuracy. These approaches check web application 
logic~\cite{felmetsger:usec10}, Android applications~\cite{flowdroid:pldi14}, 
cross checking security APIs~\cite{srivastava:pldi11}, and verifying the 
Linux Security Module~\cite{zhang:usenix:sec02}. \xxx's analysis is 
complementary to these approaches; \xxx can be further integrated with these 
approaches to track concurrency attacks.

% Specific modules/apps.
%   Toward Automated ... web applications: specific web applications.
%   Vetting SSL ...: only for SSL APIs.
%   FlowDroid: leverage Android lifecycle to improve precisions.
%   A security Policy Oracle: spefic API cross checking.
%   CQual: LSM only.
% 
% General programs.
%   Modeling and Discovering ... Property Graphs: can not reason about 
% concurrency (races), intra-procedural.
%   finding Security vulnerabilities ... Static Analysis, Lam: no control flow 
% analysis, may miss the libsafe bugs. Do not handle control-flow indirect 
% propagations.

\noindent {\bf Symbolic execution.} Symbolic execution is an advanced program
analysis technique that can systematically explore a program's execution paths
to find bugs. Researchers have built scalable and effective symbolic execution 
systems to detect software 
bugs~\cite{dart:pldi,cute:fse,godefroid:grammar-fuzzing,
godefroid:whitebox-fuzzing,
klee:osdi08,yang:malicious-disk:oakland06,cadar:exe:ccs06,s2e:hotdep09,
taas:socc10, ucklee:usec15}, block malicious 
inputs~\cite{castro:bouncer}, preserve privacy in error 
reports~\cite{castro:bug-report-privacy}, and detect programming rule 
violations~\cite{woodpecker:asplos13}. Specifically, 
UCKLEE~\cite{ucklee:usec15} has been shown to effectively detect hundreds of 
security vulnerabilities in widely used programs. Symbolic execution 
is orthogonal to \xxx; it can augment \xxx's input hints by automatically 
generating concrete vulnerable inputs.
